Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-08-21 cc/sign_relation.tex
another paper
typos found by LanguageTool

Now that we are familiar with the \pcc{} problem and its numerous applications, let us return to the
original problem of this chapter, predicting the edge sign of a signed graph. In order to do so, we
will first focus on the case where a signed graph has no disagreement (that is the minimum of
\eqref{eq:mind} is $0$) and is unweighted, as it highlights more clearly the connection with the
balance theory. We focus here on balance theory, for it is both compelling and well established.
Indeed, as illustrated by the account of \textcite{CSBalanceSurvey15}, it has been used extensively
in the last half century to study signed networks\marginpars{It was even used to study fairy
tales~\autocite{fairyTales80}.} and their dynamics.
However, it has shortcomings, the main one being its inability to deal with directed graphs.
Therefore alternative theories governing signs formation have been proposed, as surveyed
in~\autocite{Yap2015}.

@@

It is interesting to note that this local property of triangles gives raise to a global structure.
Namely a strongly balanced complete graph can be split in two (possibly empty) clusters $L$ and $R$
such that all edges within $L$ and $R$ are positive, while all edges between $L$ and $R$ are
negative. Indeed let us pick an arbitrary node $u$ and let $L=\neip(u)\setminus \{u\}$ and $R=V\setminus L$. Now
let $v,w\in L\setminus \{u\}$ and $x,y\in R$. From \autoref{fig:cc_twostrongcc} and the fact that
every triangle is balanced, we can see that $(v,w)$ and $(x,y)$ are positive edges, while $(w,y)$ is
a negative edge.
\begin{marginfigure}
  \centering
  \includegraphics[width=28mm]{assets/raw/2cc.pdf}
  \caption{A two-clustering a complete strongly balanced graph}
  \label{fig:cc_twostrongcc}
\end{marginfigure}
As we will see later, these two facts are actually equivalent.

@@

In that case as well, the local property of triangles has structural implication for the whole graph.
Namely, we can partition a complete weakly balanced graph into $k$ clusters of positively connected
nodes that are negatively tied with the rest of the graph. Consider the same construction as in
\autoref{fig:cc_twostrongcc}, putting a node $u$ and its positive neighborhood in one cluster $L$ and
the rest of the nodes in $R$. For $v,w\in L\setminus \{u\}$ and $x,y\in R$, we can still conclude
that $(v,w)$ is positive and $(v,y)$ is negative. On the other hand, this time weak balance allows
$(x,y)$ to be either positive or negative. We can split $R$ further into the positive neighborhood of
$x$ and the rest, and keep doing so until we form the $k$ clusters. We will make this argument more
formal in the following.

@@

The same results also hold for weak balance.
\begin{theorem}
  A graph $G=(V,E)$ is weakly balanced if and only if $V$ can be divided in $k$ disjoint clusters
  such that all edges within clusters are positive and all edges between clusters are negative.
\end{theorem}
\begin{proof}
  Let first assume that $G$ is weakly balanced. According to the definition, we can choose sign for
  the missing edges such that it becomes a complete graph with all its triangles weakly balanced. As
  mentioned earlier, we can then pick a node $u_1$ and let $C_1 = \neip(u) \cup \{u\}$. All
  nodes in $C_1$ are connected positively with each other and negatively with nodes in $V\setminus
  C_1$. Note also that $|V\setminus C_1| < |V|$ and therefore we can repeat this
  procedure until $V$ is exhausted, at which point we have obtained our $k$ clusters verifying the
  theorem's statement conditions.

@@

In real data though, we do not expect neither strong nor weak balance to hold, for they are fairly
demanding model. Indeed, three of the real networks considered in \autoref{chap:troll} have been
repeatedly shown to be unbalanced, although the extent of this unbalance depends of the importance
given to longer cycles compared with triads~\autocites{Facchetti2011isingmodel}{measureUnbalance14}%
{measureUnbalance17}. For the same reason, in virtually any real instances of the \pcc{} problem, the%
% there are also \url{https://arxiv.org/abs/1509.04037} about measuring balance (or frustration
% index) which they claimed has been peer reviewed?
\marginpars{The proof makes essential use of the strong balance (which is ok since next section also
deal with 2-CC) and the completeness of the graph (which is a far less realistic assumption) yet
it would be interesting to see if it can be extended.}
optimal solution will incur some disagreements. \Textcite[Section 5.5]{BookKleinberg2010}
nonetheless prove that even when only a fraction of the triangle are strongly balanced in a complete
graph, the two clusters structure is still present, although it does not cover the whole graph
anymore.

@@

We can conclude that balance theory helps characterize zero disagreement instances of \pcc{}.
However, how is \pcc{} useful in predicting edge sign? At first sight, the two problems seem to be quite
different, for the former is an unsupervised/agnostic clustering problem, while the latter is a
supervised classification problem. Yet, getting an optimal solution of \pcc{} on the training set
would provide a principled heuristics for \esp{}. Unfortunately, as we shall see in
\autoref{sub:state_of_the_art}, exact or fixed parameter solutions are not scalable and one has to
rely on approximations. Under the Unique Games Conjecture, the approximation factor is lower bounded by
$\Theta(\log n)$ in the worst case. However, this is still a viable option, as our bias is that we
will operate on instances that are to some extent balanced. Therefore, we are not in the worst case
and we can find some comfort in results about the noisy (\vpageref{sub:variants_and_extensions}) and
stable (\autoref{ssub:cc_under_stability_assumption}) settings.

>>>>

Now that we are familiar with the \pcc{} problem and its numerous applications, let us return to the
original problem of this chapter, predicting the edge sign of a signed graph. In order to do so, we
will first focus on the case where a signed graph has no disagreement (that is the minimum of
\eqref{eq:mind} is $0$) and is unweighted, as it highlights more clearly the connection with the
balance theory. We focus here on balance theory, for it is both compelling and well-established.
Indeed, as illustrated by the account of \textcite{CSBalanceSurvey15}, it has been used extensively
in the last half century to study signed networks\marginpars{It was even used to study fairy
tales~\autocite{fairyTales80}.} and their dynamics.
However, it has shortcomings, the main one being its inability to deal with directed graphs.
Therefore, alternative theories governing signs formation have been proposed, as surveyed
in~\autocite{Yap2015}.

@@

It is interesting to note that this local property of triangles gives raise to a global structure.
Namely, a strongly balanced complete graph can be split in two (possibly empty) clusters $L$ and $R$
such that all edges within $L$ and $R$ are positive, while all edges between $L$ and $R$ are
negative. Indeed, let us pick an arbitrary node $u$ and let $L=\neip(u)\setminus \{u\}$ and $R=V\setminus L$. Now
let $v,w\in L\setminus \{u\}$ and $x,y\in R$. From \autoref{fig:cc_twostrongcc} and the fact that
every triangle is balanced, we can see that $(v,w)$ and $(x,y)$ are positive edges, while $(w,y)$ is
a negative edge.
\begin{marginfigure}
  \centering
  \includegraphics[width=28mm]{assets/raw/2cc.pdf}
  \caption{A two-clustering a complete strongly balanced graph}
  \label{fig:cc_twostrongcc}
\end{marginfigure}
As we will see later, these two facts are actually equivalent.

@@

In that case as well, the local property of triangles has structural implication for the whole graph.
Namely, we can partition a complete weakly balanced graph into $k$ clusters of positively connected
nodes that are negatively tied with the rest of the graph. Consider the same construction as in
\autoref{fig:cc_twostrongcc}, putting a node $u$ and its positive neighborhood in one cluster $L$ and
the rest of the nodes in $R$. For $v,w\in L\setminus \{u\}$ and $x,y\in R$, we can still conclude
that $(v,w)$ is positive and $(v,y)$ is negative. On the other hand, this time weak balance allows
$(x,y)$ to be either positive or negative. We can split $R$ further into the positive neighborhood of
$x$ and the rest, and keep doing so until we form the $k$ clusters. In the following we will make
this argument more formal.

@@

Similar results also hold for weak balance.
\begin{theorem}
  A graph $G=(V,E)$ is weakly balanced if and only if $V$ can be divided in $k$ disjoint clusters
  such that all edges within clusters are positive and all edges between clusters are negative.
\end{theorem}
\begin{proof}
  Let first assume that $G$ is weakly balanced. According to the definition, we can choose sign for
  the missing edges such that it becomes a complete graph with all its triangles weakly balanced. As
  mentioned earlier, we can then pick a node $u_1$ and let $C_1 = \neip(u) \cup \{u\}$. All
  nodes in $C_1$ are connected positively with each other and negatively with nodes in $V\setminus
  C_1$. Note also that $|V\setminus C_1| < |V|$ and therefore we can repeat this
  procedure until $V$ is exhausted, at which point we have obtained our $k$ clusters verifying the
  theorem's statement conditions.

@@

In real data though, we do not expect either strong or weak balance to hold, for they are fairly
demanding model. Indeed, three of the real networks considered in \autoref{chap:troll} have been
repeatedly shown to be unbalanced, although the extent of this unbalance depends on the importance
given to longer cycles compared with triads~\autocites{Facchetti2011isingmodel}{measureUnbalance14}%
{measureUnbalance17}. For the same reason, in virtually any real instances of the \pcc{} problem, the%
% there are also \url{https://arxiv.org/abs/1509.04037} about measuring balance (or frustration
% index) which they claimed has been peer reviewed?
\marginpars{The proof makes essential use of the strong balance (which is ok since next section also
deal with 2-CC) and the completeness of the graph (which is a far less realistic assumption) yet
it would be interesting to see if it can be extended.}
optimal solution will incur some disagreements. \Textcite[Section 5.5]{BookKleinberg2010}
nonetheless prove that even when only a fraction of the triangle are strongly balanced in a complete
graph, the two clusters structure is still present, although it does not cover the whole graph
any more.

@@

We can conclude that balance theory helps characterize zero disagreement instances of \pcc{}.
However, how is \pcc{} useful in predicting edge sign? At first sight, the two problems seem to be quite
different, for the former is an unsupervised/agnostic clustering problem, while the latter is a
supervised classification problem. Yet, getting an optimal solution of \pcc{} on the training set
would provide a principled heuristic for \esp{}. Unfortunately, as we shall see in
\autoref{sub:state_of_the_art}, exact or fixed parameter solutions are not scalable and one has to
rely on approximations. Under the Unique Games Conjecture, the approximation factor is lower bounded by
$\Theta(\log n)$ in the worst case. However, this is still a viable option, as our bias is that we
will operate on instances that are to some extent balanced. Therefore, we are not in the worst case
and we can find some comfort in results about the noisy (\vpageref{sub:variants_and_extensions}) and
stable (\autoref{ssub:cc_under_stability_assumption}) settings.

### 2017-08-21 cc/variants.tex
typos found by LanguageTool

So far we focused on \pcc{} in its rawest form, that is solving the \mind{} and \maxa{} objectives
in the case where the general binary-labeled graph is known in advance. We will now see first some
special cases, namely when the weights obey the triangle inequality (to solve \msc{}) or when the
graph is bipartite and then move to variants. We will consider more general objectives, when the
edges are labeled categorically instead of binary, when nodes can belong simultaneously to several
cluster or when we optimize local objectives per nodes instead of global ones. We will also look at
clustering in signed graphs in general, using spectral methods or heuristics from the community
detection literature. Finally we will shift perspective and review methods beyond the batch case and
the worst-case analysis.

@@

Bipartite graphs are an interesting special case for \pcc{}, as they often appear in the context of
recommendation systems, where users rate products positively or negatively, although in this setting
we cannot expect to have complete bipartite graphs in practice. The first results was given by
\textcite{Amit04}, who obtains a $11$-approximation for \mind{} by adapting the \regionGrow{} method.
The \ccpivot{} is adapted to the bipartite case by
\textcite{Bipartite12}, who prove it results in a randomized $4$-approximation (and provide a matching
deterministic approximation by rounding a LP). By using their idea of rounding the results of the LP
differently for positive, negative and in that case same-side absent edges, \textcite{Chawla2014}
bring down this approximation factor to $3$, even for $K\geq 2$-partite graphs. By formulating the
\maxa{}$[k]$ problem as a bilinear maximization problem and computing a low-rank approximation of
the graph biadjacency matrix, \textcite{Asteris2016} obtain a efficient PTAS, that is a $(1-\delta)$
approximation running in time exponential in $k$ and $\delta^{-1}$ but linear in $n$. By an
appropriate choice of $k$, it is possible to use this PTAS to solve the general \maxa{} problem.

@@

In the so called \textsc{Chromatic}-\pcc{} setting, \enquote{positive} edges are now associated with
one of $L$ possible colors and the goal is to form clusters mostly made up of edges with the one same
color. Namely, a disagreement is now a negative edge between clusters or a within-cluster edge
whose color differs from the majority color of that cluster. This is motivated by edge-labeled graph
in social networks, biology and citation networks and will discuss such applications in
\autoref{chap:vector}. As a generalisation of \pcc{}, it is \NPc{} but \textcite{Bonchi2012a}
present a modification of the \ccpivot{} algorithm that pick edges instead of nodes as pivots, and
grow clusters by adding monochromatic triangles. This gives an approximation factor of six times the
maximum degree of the graph. They also present a method when the number $k$ of clusters is fixed
beforehand, starting with an initial partition and then alternating between finding the majority
color of clusters and finding better clusters. Unfortunately, the maximum degree of a graph can be
as large as $n$. However, \textcite{Anava2015} present constant factor approximations. Namely, they
show the problem can be reduce to classical \pcc{} by setting all edges incident to a node $u$ to
negative if they are not of the majority color of $u$. They then apply the regular \ccpivot{} and
show this gives a $11$-approximation to the original problem. Furthermore, they also write a linear
program and round it using the \regionGrow{} method to obtain an
approximation factor of $4$. \Textcite{multiChromatic15} extend this line of work to the case were a
single edge can carry a \emph{set} of labels and adapt their randomized algorithm so that the
approximation factor is multiplied by the size of the input label set.

@@

While in \pcc{}, each node is assigned to a single cluster, in other settings we may want to relax
this constraint. Given a complete weighted graph, \textcite{Bonchi2012} want to output a clustering
\cluster{} that minimizes the following cost: \[ \sum_{(u,v)\in E} \left| H(\cluster(u),
\cluster(v)) - w_{uv}\right|\] where $H$ is a similarity function between two sets of labels, chosen
here to be the Jaccard similarity or a $0/1$ indicator of non empty intersection. These problems are
showed \NPc{} and approximated by a local search algorithm, iteratively optimizing the assignment of
one node while all others are fixed. As one of the demonstration on their theoretical work,
\textcite{WeightedTheta15} show a faster solution based on a weighted extension of the Lovász's
theta function, the corresponding geometric embedding of graphs and a solver derived from one-class
SVM, while \textcite{GeneticOCC14} propose a genetic algorithm to solve this problem. Finally,
\Textcite{StochasticCC13} also deals with overlapping clustering by relaxing the problem to a
stochastic setting and using \enquote{the Baum-Eagon inequality, which provides an effective
iterative means for maximizing polynomial functions in probability domains}.

@@

Given a function $f: \Rbb^n_{\geq 0} \rightarrow \Rbb$ verifying two elementary conditions, the
problem is then to find a fractional clustering $x$ minimizing $f(err(x))$. The classical \pcc{}
corresponds to setting $f(x) = \lhalf{}\ell^1(x)$ whereas the authors here are interested in Minimax
\pcc{} that arises by setting $f(x) = \ell^\infty(x)$. Minimizing the maximum number of
disagreements incurred by a single node is motivated by the example of recommendation systems: if
errors correspond to unsatisfying recommendations, we do not want a single user to suffer a large
number of them. Minimax \pcc{} is \NPc{} on both complete graphs and complete bipartite graphs but
by modifying the \regionGrow{} method, the authors respectively a $48$ and
$10$ approximation, the latter for the one-sided error (that only counts disagreements for the nodes
in one of the two clusters).
The idea is to chose pivot not randomly but by maximizing a given criteria and
to grow balls with a radius $\alpha$ computed numerically to optimize the approximation factor.
Interestingly, and in contrast with the classic \pcc{} situation, minimax \maxa{} is not easier than
minimax \mind{} and seems not to have a constant factor approximation, even on complete graphs.
Furthermore, these algorithms are deterministic, as opposed to many \pcc{} approximation, since
bounds on expected disagreements of an edge does not translate easily on their maximum.
\Textcite{Charikar2017} improve these two factors to $7$, using a simpler version of the algorithm
of \textcite{pmlr-v48-puleo16}. Namely, find the ball of radius $\nicefrac{1}{7}$ with the largest
number node and create a cluster from its center with a radius of $\nicefrac{3}{7}$. They also show
that on general weighted graphs, the LP has a large integrality gap of $\nicefrac{n}{2}$ yet they
combine it with a combinatorial approach to reach a $O(\sqrt{n})$ approximation. Finally they
consider the complementary problem of maximizing the minimum number of agreements reach at a single
node, and provide a $\frac{1}{2+\epsilon}$ approximation.

@@

Letting \ncut{}$(C, \bar{C}) = \frac{\mathrm{cut}(C, \bar{C})}{\mathrm{bal}(C)}$ with
$\mathrm{bal}(C) = 2\frac{vol(C)vol(\bar{C})}{vol(V)}$, \textcite{mOneCC12} define a new objective:
\begin{equation*}
  \hat{F}_\gamma(C) = \frac{\mathrm{cut}(C, \bar{C}) + \gamma\left(\hat{M}(C)+\hat{N}(C)\right)}{\mathrm{bal}(C)}
\end{equation*}
where $\gamma \in \Rbb{}_+$ is a parameter, while $\hat{M}(C)$ and $\hat{N}(C)$ are respectively the
number of positive and negative disagreements of the $(C, \bar{C})$ clustering.
They show how to optimize a tight continuous relaxation of $\hat{F}_\gamma$ as the non negative
ratio of a difference of convex function and a convex function.

@@

The clustering problem is often named community detection in the context of social networks, and
several methods developed by practitioners have been extended to signed graphs. While they do not
necessarily considered the \pcc{} objective, and especially not its optimum, we still give a brief
overview of them, as they tend to have been more tested experimentally. For instance, to find the
cluster of node $u$, \textcite{Yang2007} use a random walk approach on the positive subgraph $G^+$
to compute the probability of each node to reach $u$ in $T$ steps, sort the nodes accordingly and
then find a threshold  based on the number of disagreements.
The one node moves local heuristic that we described in the Physics-inspired paragraph
\vpageref{par:cc_physics} can also be formulated as genetic algorithms that simultaneously try to
minimize the number of disagreements and maximize a signed variant of the
modularity~\autocites{Li2013}{Amelio2013}. \Textcite{Anchuri2012} also consider these two objectives
by seeing them as eigenvalue problems and devise a iterative splitting procedure.
The overlapping community detection variant is considered by \textcite{Chen14}, who used a signed
probabilistic mixture model. Namely, an edge selects a pair of cluster $r,s$ with probability
$\omega_{rs}$ (where $r=s$ if the edge is positive and $r\neq s$ otherwise) and chooses its endpoints
$u$ and $v$ with probability $\theta_{ru}$ and $\theta_{sv}$. $\theta_{ru}$ is therefore the soft
membership of node $u$ to cluster $r$, and those parameters are estimated using the
expectation-maximization algorithm. The same model is extended to directed graphs by
\textcite{Jiang2015}, who strangely enough names it stochastic blockmodel, although the focus is
still on edge and not nodes.
In a similar spirit to \maxa{}$[k]$, \textcite{SignedGang} focus on finding $k$ subgraphs dense in
positive edges and densely connected by negative edges to each others. They dub such subgraph
\emph{Oppositive Cohesive Groups}, or more vividly \emph{Gangs in War}, and after formulating the
problem as a constrained quadratic optimization, they propose a faster iterative local search
heuristic.
% relaxed structural balance \autocite{Doreian2009} but used the same approach as \textcite{Early96}

@@

Case in point, in the context of entity resolution, \textcite{activeCoref07} consider the \pcc{}
problem where by querying an oracle, one can either reduce the uncertainty about one edge weight or
add an extra node with edges connecting it to existing nodes. However, this requires web queries
that are resource bounded and thus yields an active setting learning problem, where one has to
choose the most informative
queries given a budget. A formal definition is given in~\autocite{queryMoreEdgeCC07} and in
practice, after finding an initially good partition, they select in each cluster a node to be its
centroid, and query the edges connecting the centroid as ordered by an entropy-based criterion.
In the case the oracle answering the queries is consistent, then they exists an information
theoretic bound on the number of queries needed to recover the clusters, and an algorithm matching
that bound up to a $O(\log n)$ factor~\autocite{perfectActiveLong17}.
\textcite[Section 5]{Ailon2014} present another active algorithm that solves \mind$[k]$ with a
linear number of queries but an exponential running time in $n$.  In a noisy setting,
\textcite{Mitzenmacher2016} assume there is a planted $k$-partition and that we have access to an
oracle that for $u,v\in V^2$ returns $\cluster(u) - \cluster(v) \mod k$ with probability $1-p$ and a
noisy $\cluster(u) - \cluster(v) \pm 1 \mod k$ otherwise. For $k=2$, this is exactly $2$-\pcc{},
whereas for $k>2$, the oracle gives more information than simply the sign of the path from $u$ to
$v$. Whenever
$p < \shalf$, they show that $O(n^{1+\frac{1}{\log\log n}}\log n)$ queries are enough are to recover
the planted partition in polynomial time and with high probability. Those queries are actually
random (\ie{} non-adaptive), and the clusters are found by looking at almost edge-disjoint path
between all pairs of nodes.

In the online setting, \textcite{greedyOnline10} give a greedy algorithm that upon node arrival creates a
singleton cluster and then merge all pairs of clusters for which it increases the total number of
agreements. For \mind{}, this is $O(n)$-competitive algorithm and they show such ratio is optimal by
exhibiting an instance\footnote{Namely two positive cliques $A$ and $B$ joined by positive edges except
between $a\in A$ and $\{b_1,\ldots, b_k\}\in B$. Those nodes are given first and thus form a cluster,
which yields at least one disagreement every time one the $n-(k+1)$ remaining nodes is added.} on
which any strategy ends up with $n - k$ disagreements whereas optimal cost is $k$. On the \maxa{}
side, this greedy strategy result in a $\shalf$-competitive algorithm. If it is randomly mixed with a
\textsc{Dense} variation, it increases to $\shalf+\eta$, still far from the demonstrated $0.834$ upper
bound.
% when the graph is given node by node,
% \url{https://link.springer.com/chapter/10.1007/978-3-319-18173-8_7} show to cluster it in static
% clique, so it sounds related to cluster editing, except their objective is to maximize the
% fraction of edge in cliques (ie avoid small cluster)

>>>>

So far we focused on \pcc{} in its rawest form, that is solving the \mind{} and \maxa{} objectives
in the case where the general binary-labeled graph is known in advance. We will now see first some
special cases, namely when the weights obey the triangle inequality (to solve \msc{}) or when the
graph is bipartite and then move to variants. We will consider more general objectives, when the
edges are labeled categorically instead of binary, when nodes can belong simultaneously to several
clusters or when we optimize local objectives per nodes instead of global ones. We will also look at
clustering in signed graphs in general, using spectral methods or heuristics from the community
detection literature. Finally, we will shift perspective and review methods beyond the batch case and
the worst-case analysis.

@@

Bipartite graphs are an interesting special case for \pcc{}, as they often appear in the context of
recommendation systems, where users rate products positively or negatively, although in this setting
we cannot expect to have complete bipartite graphs in practice. The first results was given by
\textcite{Amit04}, who obtains an $11$-approximation for \mind{} by adapting the \regionGrow{} method.
The \ccpivot{} is adapted to the bipartite case by
\textcite{Bipartite12}, who prove it results in a randomized $4$-approximation (and provide a matching
deterministic approximation by rounding a LP). By using their idea of rounding the results of the LP
differently for positive, negative and in that case same-side absent edges, \textcite{Chawla2014}
bring down this approximation factor to $3$, even for $K\geq 2$-partite graphs. Through formulating the
\maxa{}$[k]$ problem as a bilinear maximization problem and computing a low-rank approximation of
the graph biadjacency matrix, \textcite{Asteris2016} obtain a efficient PTAS, that is a $(1-\delta)$
approximation running in time exponential in $k$ and $\delta^{-1}$ but linear in $n$. By an
appropriate choice of $k$, it is possible to use this PTAS to solve the general \maxa{} problem.

@@

In the so called \textsc{Chromatic}-\pcc{} setting, \enquote{positive} edges are now associated with
one of $L$ possible colors and the goal is to form clusters mostly made up of edges with the one same
color. Namely, a disagreement is now a negative edge between clusters or a within-cluster edge
whose color differs from the majority color of that cluster. This is motivated by edge-labeled graph
in social networks, biology and citation networks and will discuss such applications in
\autoref{chap:vector}. As a generalisation of \pcc{}, it is \NPc{} but \textcite{Bonchi2012a}
present a modification of the \ccpivot{} algorithm that pick edges instead of nodes as pivots, and
grow clusters by adding monochromatic triangles. This gives an approximation factor of six times the
maximum degree of the graph. They also present a method when the number $k$ of clusters is fixed
beforehand, starting with an initial partition and then alternating between finding the majority
color of clusters and finding better clusters. Unfortunately, the maximum degree of a graph can be
as large as $n$. However, \textcite{Anava2015} present constant factor approximations. Namely, they
show the problem can be reduced to classical \pcc{} by setting all edges incident to a node $u$ to
negative if they are not of the majority color of $u$. They then apply the regular \ccpivot{} and
show this gives an $11$-approximation to the original problem. Furthermore, they also write a linear
program and round it using the \regionGrow{} method to obtain an
approximation factor of $4$. \Textcite{multiChromatic15} extend this line of work to the case were a
single edge can carry a \emph{set} of labels and adapt their randomized algorithm so that the
approximation factor is multiplied by the size of the input label set.

@@

While in \pcc{}, each node is assigned to a single cluster, in other settings we may want to relax
this constraint. Given a complete weighted graph, \textcite{Bonchi2012} want to output a clustering
\cluster{} that minimizes the following cost: \[ \sum_{(u,v)\in E} \left| H(\cluster(u),
\cluster(v)) - w_{uv}\right|\] where $H$ is a similarity function between two sets of labels, chosen
here to be the Jaccard similarity or a $0/1$ indicator of nonempty intersection. These problems are
showed \NPc{} and approximated by a local search algorithm, iteratively optimizing the assignment of
one node while all others are fixed. As one of the demonstration on their theoretical work,
\textcite{WeightedTheta15} show a faster solution based on a weighted extension of the Lovász's
theta function, the corresponding geometric embedding of graphs and a solver derived from one-class
SVM, while \textcite{GeneticOCC14} propose a genetic algorithm to solve this problem. Finally,
\Textcite{StochasticCC13} also deals with overlapping clustering by relaxing the problem to a
stochastic setting and using \enquote{the Baum-Eagon inequality, which provides an effective
iterative scheme for maximizing polynomial functions in probability domains}.

@@

Given a function $f: \Rbb^n_{\geq 0} \rightarrow \Rbb$ verifying two elementary conditions, the
problem is then to find a fractional clustering $x$ minimizing $f(err(x))$. The classical \pcc{}
corresponds to setting $f(x) = \lhalf{}\ell^1(x)$ whereas the authors here are interested in Minimax
\pcc{} that arises by setting $f(x) = \ell^\infty(x)$. Minimizing the maximum number of
disagreements incurred by a single node is motivated by the example of recommendation systems: if
errors correspond to unsatisfying recommendations, we do not want a single user to suffer many
of them. Minimax \pcc{} is \NPc{} on both complete graphs and complete bipartite graphs but
by modifying the \regionGrow{} method, the authors respectively a $48$ and
$10$ approximation, the latter for the one-sided error (that only counts disagreements for the nodes
in one of the two clusters).
The idea is to chose pivots not randomly but by maximizing a given criteria and
to grow balls with a radius $\alpha$ computed numerically to optimize the approximation factor.
Interestingly, and in contrast with the classic \pcc{} situation, minimax \maxa{} is not easier than
minimax \mind{} and seems not to have a constant factor approximation, even on complete graphs.
Furthermore, these algorithms are deterministic, as opposed to many \pcc{} approximations, since
bounds on expected disagreements of an edge does not translate easily on their maximum.
\Textcite{Charikar2017} improve these two factors to $7$, using a simpler version of the algorithm
of \textcite{pmlr-v48-puleo16}. Namely, find the ball of radius $\nicefrac{1}{7}$ with the largest
number node and create a cluster from its center with a radius of $\nicefrac{3}{7}$. They also show
that on general weighted graphs, the LP has a large integrality gap of $\nicefrac{n}{2}$ yet they
combine it with a combinatorial approach to reach a $O(\sqrt{n})$ approximation. Finally, they
consider the complementary problem of maximizing the minimum number of agreements reach at a single
node, and provide a $\frac{1}{2+\epsilon}$ approximation.

@@

Letting \ncut{}$(C, \bar{C}) = \frac{\mathrm{cut}(C, \bar{C})}{\mathrm{bal}(C)}$ with
$\mathrm{bal}(C) = 2\frac{vol(C)vol(\bar{C})}{vol(V)}$, \textcite{mOneCC12} define a new objective:
\begin{equation*}
  \hat{F}_\gamma(C) = \frac{\mathrm{cut}(C, \bar{C}) + \gamma\left(\hat{M}(C)+\hat{N}(C)\right)}{\mathrm{bal}(C)}
\end{equation*}
where $\gamma \in \Rbb{}_+$ is a parameter, while $\hat{M}(C)$ and $\hat{N}(C)$ are respectively the
number of positive and negative disagreements of the $(C, \bar{C})$ clustering.
They show how to optimize a tight continuous relaxation of $\hat{F}_\gamma$ as the non-negative
ratio of a difference of convex function and a convex function.

@@

The clustering problem is often named community detection in the context of social networks, and
several methods developed by practitioners have been extended to signed graphs. While they do not
necessarily considered the \pcc{} objective, and especially not its optimum, we still give a brief
overview of them, as they tend to have been more tested experimentally. For instance, to find the
cluster of node $u$, \textcite{Yang2007} use a random walk approach on the positive subgraph $G^+$
to compute the probability of each node to reach $u$ in $T$ steps, sort the nodes accordingly and
then find a threshold  based on the number of disagreements.
The one node moves local heuristic that we described in the Physics-inspired paragraph
\vpageref{par:cc_physics} can also be formulated as genetic algorithms that simultaneously try to
minimize the number of disagreements and maximize a signed variant of the
modularity~\autocites{Li2013}{Amelio2013}. \Textcite{Anchuri2012} also consider these two objectives
by seeing them as eigenvalue problems and devise a iterative splitting procedure.
The overlapping community detection variant is considered by \textcite{Chen14}, who used a signed
probabilistic mixture model. Namely, an edge selects a pair of cluster $r,s$ with probability
$\omega_{rs}$ (where $r=s$ if the edge is positive and $r\neq s$ otherwise) and chooses its endpoints
$u$ and $v$ with probability $\theta_{ru}$ and $\theta_{sv}$. $\theta_{ru}$ is therefore the soft
membership of node $u$ to cluster $r$, and those parameters are estimated using the
expectation-maximization algorithm. The same model is extended to directed graphs by
\textcite{Jiang2015}, who strangely enough names it stochastic blockmodel, although the focus is
still on edge and not nodes.
In a similar spirit to \maxa{}$[k]$, \textcite{SignedGang} focus on finding $k$ subgraphs dense in
positive edges and densely connected by negative edges to each other. Thee dub such subgraph
\emph{Oppositive Cohesive Groups}, or more vividly \emph{Gangs in War}, and after formulating the
problem as a constrained quadratic optimization, they propose a faster iterative local search
heuristic.
% relaxed structural balance \autocite{Doreian2009} but used the same approach as \textcite{Early96}

@@

Case in point, in the context of entity resolution, \textcite{activeCoref07} consider the \pcc{}
problem where, by querying an oracle, one can either reduce the uncertainty about one edge weight or
add an extra node with edges connecting it to existing nodes. However, this requires web queries
that are resource bounded and thus yields an active setting learning problem, where one has to
choose the most informative
queries given a budget. A formal definition is given in~\autocite{queryMoreEdgeCC07} and in
practice, after finding an initially good partition, they select in each cluster a node to be its
centroid, and query the edges connecting the centroid as ordered by an entropy-based criterion.
In the case the oracle answering the queries is consistent, then there exists an information
theoretic bound on the number of queries needed to recover the clusters, and an algorithm matching
that bound up to a $O(\log n)$ factor~\autocite{perfectActiveLong17}.
\textcite[Section 5]{Ailon2014} present another active algorithm that solves \mind$[k]$ with a
linear number of queries but an exponential running time in $n$.  In a noisy setting,
\textcite{Mitzenmacher2016} assume there is a planted $k$-partition and that we have access to an
oracle that for $u,v\in V^2$ returns $\cluster(u) - \cluster(v) \mod k$ with probability $1-p$ and a
noisy $\cluster(u) - \cluster(v) \pm 1 \mod k$ otherwise. For $k=2$, this is exactly $2$-\pcc{},
whereas for $k>2$, the oracle gives more information than simply the sign of the path from $u$ to
$v$. Whenever
$p < \shalf$, they show that $O(n^{1+\frac{1}{\log\log n}}\log n)$ queries are enough are to recover
the planted partition in polynomial time and with high probability. Those queries are actually
random (\ie{} non-adaptive), and the clusters are found by looking at almost edge-disjoint path
between all pairs of nodes.

In the online setting, \textcite{greedyOnline10} give a greedy algorithm that upon node arrival creates a
singleton cluster and then merge all pairs of clusters for which it increases the total number of
agreements. For \mind{}, this is $O(n)$-competitive algorithm and they show such ratio is optimal by
exhibiting an instance\footnote{Namely, two positive cliques $A$ and $B$ joined by positive edges except
between $a\in A$ and $\{b_1,\ldots, b_k\}\in B$. Those nodes are given first and thus form a cluster,
which yields at least one disagreement every time one the $n-(k+1)$ remaining nodes is added.} on
which any strategy ends up with $n - k$ disagreements whereas optimal cost is $k$. On the \maxa{}
side, this greedy strategy result in a $\shalf$-competitive algorithm. If it is randomly mixed with a
\textsc{Dense} variation, it increases to $\shalf+\eta$, still far from the demonstrated $0.834$ upper
bound.
% when the graph is given node by node,
% \url{https://link.springer.com/chapter/10.1007/978-3-319-18173-8_7} show to cluster it in static
% clique, so it sounds related to cluster editing, except their objective is to maximize the
% fraction of edge in cliques (ie avoid small cluster)
